Case study validations of automatic bullet matching

### 2018-11-09 index.Rmd
rephrase a bit and cite the paper.

\begin{itemize}
\item[(a)] Identify an area on the LEA, striae are expressed. 
XXXX get from area to crosscut XXXX
\hh{
Let $z(t)$ describe a digitized toolmark for the striation marks on a land engraved area.
$z(t)$ is then a spatial process indexed by $t$, where $t, t = 1,...,T$ denotes equally spaced pixel locations for a total length of $T$. }

>>>>

\begin{itemize}
\item[(a)] Identify an area on the LEA with expressed striae. Locate a stable crosscut (see \citet{aoas}) in the identified area. 
<!-- XXXX get from area to crosscut XXXX -->
<!-- \hh{ -->
<!-- Let $z(t)$ describe a digitized toolmark for the striation marks on a land engraved area. -->
<!-- $z(t)$ is then a spatial process indexed by $t$, where $t, t = 1,...,T$ denotes equally spaced pixel locations for a total length of $T$. } -->
